---
title: 'Search Audit Report: Florida and Hawaii Queries'
output:
  pdf_document: default
  html_document:
    df_print: paged
  github_document:
    toc: true
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

knitr::opts_knit$set(root.dir = "~/Github/Lab_Legal_Design/search_audit")
```

```{r include=FALSE}
library(tidyverse)
library(tidytext)
library(stringr)

# get the ultimate directory
# has format "[states]_audit_[month]_[year]
# must exist as a folder in processed_data/
which_audit <- "FL_HI_audit_Jan_2020"

all_tables <- 
  str_glue("processed_data/", which_audit, "/all_queries_filtered.csv") %>%
  read_csv(
    col_types = cols(
        .default = col_character(),
        sub_rank = col_double(),
        cmpt_rank = col_double(),
        serp_rank = col_double(),
        timestamp = col_character(),
        text = col_character()
    )
  )
```

```{r analysis function, echo=FALSE, message=FALSE}
# analyze all queries using this function
# gets the top 3 URL domains
# first page URL domains
# most common suffixes
# percentage ads
# most common ad domain
analysis <- function(loc, tp) {
  print(str_glue("Location: {loc}, Legal query: {tp}", loc = loc, tp = tp))
  
  sub_table <-
    all_tables %>% 
    filter(place %in% loc, legal_type == tp) %>% 
    select(place, legal_type, everything())
  
  print("Top 3 URL domains")
  sub_table %>% 
    filter(type == "general", sub_rank >= 3, !is.na(full_url)) %>%
    count(full_url, sort = TRUE) %>% 
    print()
  
  print("First page top URL domains")
  sub_table %>% 
    filter(!is.na(full_url)) %>% 
    count(full_url, sort = TRUE) %>% 
    print()
  
  print("Most common suffixes")
  sub_table %>% 
    filter(!is.na(urlsuffix)) %>% 
    count(urlsuffix, sort = TRUE) %>% 
    print()
  
  print("Percentage of ads")
  sub_table %>% 
    filter(type %in% c("ad", "general")) %>% 
    count(type) %>% 
    mutate(prop = n / sum(n) * 100) %>% 
    filter(type == "ad") %>% 
    pull(prop) %>% 
    print()
  
  print("Most common ad domain")
  sub_table %>% 
    filter(type == "ad") %>% 
    count(urldomain, sort = TRUE) 
}
``` 

## Comparison between different categories

```{r domain suffix count}
# Domain suffix count by legal type
all_tables %>% 
  filter(!is.na(urlsuffix)) %>% 
  mutate(urlsuffix = fct_lump(urlsuffix, prop = 0.03)) %>% 
  count(urlsuffix, legal_type, sort = TRUE) %>%
  mutate(
    legal_type = str_replace(legal_type, "_", " ") %>% str_to_title(),
    urlsuffix = fct_reorder(urlsuffix, n) %>% fct_rev()
  ) %>% 
  ggplot(aes(urlsuffix, n, fill = legal_type)) +
  geom_col(position = "dodge") +
  theme_minimal() +
  labs(
    title = "Domain suffix count by legal type",
    subtitle = "All queries have more .com links, but numbers are close for domestic violence",
    y = "Count",
    x = "Domain suffix",
    fill = "Legal type"
  )
```

```{r domain suffix percent}
# Domain suffix percent breakdown
all_tables %>% 
  filter(!is.na(urlsuffix)) %>% 
  mutate(urlsuffix = fct_lump(urlsuffix, prop = 0.03)) %>% 
  count(state, legal_type, urlsuffix) %>%
  group_by(state, legal_type) %>% 
  mutate(perc = n / sum(n)) %>% 
  ungroup() %>% 
  mutate(
    legal_type = str_replace(legal_type, "_", " ") %>% str_to_title(),
    urlsuffix = fct_reorder(urlsuffix, n) %>% fct_rev()
  ) %>% 
  ggplot(aes(urlsuffix, perc, fill = legal_type)) +
  geom_col(position = "dodge") +
  facet_grid(cols = vars(state)) +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    title = "Domain suffix percent breakdown",
    subtitle = str_glue(
      "Domestic violence in Hawaii has more .org links, all others have more .com links",
      "\nSpread between FL and HI are similar across all search query types"
    ),
    y = "Percent",
    x = "Domain suffix",
    fill = "Legal type"
  )
```

```{r ad percentage}
# Percent of ads on a given search page
all_tables %>% 
  filter(type %in% c("ad", "general")) %>% 
  count(type, legal_type) %>% 
  group_by(legal_type) %>% 
  mutate(prop = n / sum(n)) %>% 
  filter(type == "ad") %>% 
  ungroup() %>% 
  mutate(
    legal_type = str_replace(legal_type, "_", " ") %>% str_to_title(),
    legal_type = fct_reorder(legal_type, prop) %>% fct_rev()
  ) %>% 
  ggplot(aes(legal_type, prop)) +
  geom_col() +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    title = "Percent of ads on a given search page", 
    subtitle = str_glue(
      "Domestic violence has the largest proportion of ads, eviction queries have the least"
    ),
    x = "Legal query type",
    y = "Percent"
  ) 


all_tables %>% 
  filter(type %in% c("ad", "general")) %>% 
  count(state, type, legal_type) %>% 
  group_by(state, legal_type) %>% 
  mutate(prop = n / sum(n)) %>% 
  filter(type == "ad") %>% 
  ungroup() %>% 
  mutate(
    legal_type = str_replace(legal_type, "_", " ") %>% str_to_title(),
    legal_type = fct_reorder(legal_type, prop) %>% fct_rev()
  ) %>% 
  ggplot(aes(legal_type, prop)) +
  geom_col() +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  facet_grid(cols = vars(state)) +
  labs(
    title = "Percent of ads on a given search page", 
    subtitle = "Debt collection has the largest proportion of ads, eviction queries have the least",
    x = "Legal query type",
    y = "Percent"
  ) 
```


```{r, echo=FALSE}
# extract non-US websites, find the % of websites outside of US
all_tables %>% 
  mutate(non_us = str_extract(urlsuffix, "[^\\.]+$") %in% c("uk", "sg", "nz", "jp", "ca", "au")) %>% 
  count(legal_type, non_us) %>% 
  group_by(legal_type) %>% 
  mutate(perc = n / sum(n)) %>% 
  ungroup() %>% 
  filter(non_us == TRUE) %>% 
  mutate(
    legal_type = str_replace(legal_type, "_", "\n") %>% str_to_title(),
    legal_type = fct_reorder(legal_type, perc) %>% fct_rev()
  ) %>% 
  ggplot(aes(legal_type, perc)) +
  geom_col() +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  labs(
    title = "Percent of non-US domain names", 
    subtitle = str_glue(
      "Domestic violence has >1% links leading to non-US sites in the first Google search result page",
      "\n from Australia, UK, Canada, Singapore, and New Zealand"
    ),
    x = "Legal query type",
    y = "Percent of non-US domain names"
  ) 

all_tables %>% 
  mutate(non_us = str_extract(urlsuffix, "[^\\.]+$") %in% c("uk", "sg", "nz", "jp", "ca", "au")) %>% 
  count(state, legal_type, non_us) %>% 
  group_by(state, legal_type) %>% 
  mutate(perc = n / sum(n)) %>% 
  ungroup() %>% 
  filter(non_us == TRUE) %>% 
  mutate(
    legal_type = str_replace(legal_type, "_", "\n") %>% str_to_title(),
    legal_type = fct_reorder(legal_type, perc) %>% fct_rev()
  ) %>% 
  ggplot(aes(legal_type, perc)) +
  geom_col() +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  facet_grid(cols = vars(state)) +
  labs(
    title = "Percent of non-US domain names", 
    subtitle = str_glue(
      "Domestic violence (and eviction from Hawaii) has >1% links leading to",
      "\n  non-US sites from Australia, UK, Canada, Singapore, and New Zealand"
    ),
    x = "Legal query type",
    y = "Percent of non-US domain names"
  ) 

```

## Rural Oahu

### Debt collection

```{r, echo=FALSE}
analysis("Rural Oahu", "debt_collection")
```


### Domestic violence

```{r, echo=FALSE}
analysis("Rural Oahu", "domestic_violence")
```


### Flood contractor

```{r, echo=FALSE}
analysis("Rural Oahu", "flood_contractor")
```

### Eviction

```{r, echo=FALSE}
analysis("Rural Oahu", "eviction")
```

## Honolulu

### Debt collection

```{r, echo=FALSE}
analysis("Honolulu", "debt_collection")
```


### Domestic violence

```{r, echo=FALSE}
analysis("Honolulu", "domestic_violence")
```


### Flood contractor

```{r, echo=FALSE}
analysis("Honolulu", "flood_contractor")
```

### Eviction

```{r, echo=FALSE}
analysis("Honolulu", "eviction")
```

## Jacksonville

### Debt collection

```{r, echo=FALSE}
analysis("Jacksonville", "debt_collection")
```


### Domestic violence

```{r, echo=FALSE}
analysis("Jacksonville", "domestic_violence")
```


### Flood contractor

```{r, echo=FALSE}
analysis("Jacksonville", "flood_contractor")
```

### Eviction

```{r, echo=FALSE}
analysis("Jacksonville", "eviction")
```

## Pensacola

### Debt collection

```{r, echo=FALSE}
analysis("Pensacola", "debt_collection")
```


### Domestic violence

```{r, echo=FALSE}
analysis("Pensacola", "domestic_violence")
```


### Flood contractor

```{r, echo=FALSE}
analysis("Pensacola", "flood_contractor")
```

### Eviction

```{r, echo=FALSE}
analysis("Pensacola", "eviction")
```

## Tallahassee

### Debt collection

```{r, echo=FALSE}
analysis("Tallahassee", "debt_collection")
```


### Domestic violence

```{r, echo=FALSE}
analysis("Tallahassee", "domestic_violence")
```


### Flood contractor

```{r, echo=FALSE}
analysis("Tallahassee", "flood_contractor")
```

### Eviction

```{r, echo=FALSE}
analysis("Tallahassee", "eviction")
```

